Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-20 paper.tex
Minor changes to the manuscript

In persuit of the Moss-like relation of 2D materials, a accurate

@@

established. One known issue is that the concept of macroscopic

@@

placed at the xy-plane of a periodically repeating superlattice (SL)
with a length $L$ along the z-direction large enough to prevent the
interactions between periodic images. The macroscopic dielectric

@@

directions in $(x, y, z)$,such that:

@@

the 2D material is placed in vacuum, such that $\kappa^{pp} \equiv 1$
and $\kappa^{pq} \equiv 0$, we can distinguish two components of the

@@

extends to ~12 \AA{} along the z-direction inside the SL. When $L$ is

@@

\ref{fig-1}c \todo{change order!}, respectively. We can also observe

@@

$\boldsymbol{\mu}^{p} = \boldsymbol{P}_{p}L = \int_{\mathrm{SL}}
\rho(\boldsymbol{r}) \boldsymbol{r}_{p}d^{3} \boldsymbol{r}/A$,

@@

$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}d
and \ref{fig-1}e). These findings indicate that the 2D polarizability,

@@

  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}

@@

(details see Supplementary Section SXX \todo{mark!}):

@@

the Schr\"{o}dinger equation Hamiltonian

@@

We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using the polarizabilities calculated by first principle
calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle dots), with a
linear regression slope of ~0.182 and $R^{2}$ of 0.84. From
Ref. \cite{Jiang_2017_Eg_Eb}, the slope between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter
equation (BSE), the convergence of such method is known to be highly
affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other wordst, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

@@

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$,
\cite{Keldysh_1979_eps_multi,Pulci_2014}:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$, where $H_{0}$
is the Struve function and $Y_{0}$ is the Bessel function of second
kind, is assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994}. The in-plane screening length is generally larger
for a smaller bandgap semiconductor, which qualitatively explains the
inverse propotional relation between $\alpha^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

>>>>

In persuit of the Moss-like relation of 2D materials, an accurate

@@

established. One challenge is that the concept of macroscopic

@@

placed in the xy-plane of a periodically repeating superlattice (SL)
with a length $L$ along the z-direction. The macroscopic dielectric

@@

directions in $(x, y, z)$, such that:

@@

the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
and $\kappa^{pq} = 0$, we can distinguish two components of the

@@

extends to ~12 \AA{} along the z-direction. When $L$ is

@@

\ref{fig-1}c \todo{change order!}, respectively. We also observe

@@

$\boldsymbol{\mu}^{p} = \boldsymbol{P}^{p}L = \int_{\mathrm{SL}}
\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$,

@@

$\varepsilon_{\mathrm{SL}}^{\perp}$ of the TMDCs, as shown Figure \ref{fig-1}d
and \ref{fig-1}e, respectively. These findings indicate that the 2D polarizability,

@@

  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\boldsymbol{q}|^{2} \Omega}

@@

(details see Supplementary Section S4):

@@

the Schr\"{o}dinger equation with Hamiltonian

@@

We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using the polarizabilities calculated by first principle
calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle
dots), with a linear regression slope of ~0.182 and $R^{2}$ of
0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter
equation (BSE), the convergence of such method is known to be highly
affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other words, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

@@

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
screening length is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
version of the Moss-relation.
